Precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-17 manuscript.tex
3.2 & 3.3

Considering the number of spikes required to exceed a voltage threshold, asynchronous signals are less efficient than synchronous signals. However, taking axonal propagation times into account, synchronous signals may not coincide significantly at the post-synaptic neuron contrary to asynchronous or polychronous signals. The term polychronous was first introduced by~\citet{izhikevich_polychronization_2006}. He defines this term after pointing out a particular organization of the neurons of his spiking artificial neural network. The network is characterized by a timing-dependant learning rule for weights (STDP) and by fixed conduction delays between neurons. Due to the interplay between the delays and STDP, the spiking neurons spontaneously self-organize into groups and generate patterns of stereotypical polychronous activity, i.e.~exhibit reproducible time-locked but not synchronous firing patterns. The neurons composing a group discharge at different times, but due to delays, the spikes reach the postsynaptic neuron at the same time. This synchrony leads to the summation of the excitatory post-synaptic potentials evoked by each spike and thus to the crossing of the voltage threshold and to the discharge of a spike. According to the STDP rule, the neurons involved in this activity will see their weight of synaptic connection increase and thus, constitute a polychronous group. Interestingly, thanks to the fact that a neuron can be involved in different polychronous groups, the number of coexisting polychronous groups far exceeds the number of neurons in the network, resulting in an unprecedented memory capacity of the system.

@@

% polychronization
Interestingly the paper by~\citet{izhikevich_polychronization_2006} stirred a debate in the field of computational neuroscience, with a general postive acceptance, but quite few works extended this seminal paper.

% dynamic networks \& learning delays:

    Huning H., Glunder H., and Palm G. (1998) Synaptic delay learning in pulse-coupled neurons. Neural Computation, 10:555--565. \url{https://www.deepdyve.com/lp/mit-press/synaptic-delay-learning-in-pulse-coupled-neurons-DGMiNHxp0A}
    \href{https://www.researchgate.net/publication/37921636_Dynamics_of_Self-Organized_Delay_Adaptation}{Eurich C., Pawelzik K., Ernst U., Cowan J., and Milton J. (1999) Dynamics of self-organazed delay adaptation. Phys. Rev.~Lett., 82:1594--1597.}

A popular model for the detection of latency patterns is the tempotron~\citep{gutig_tempotron_2006}. This model is in particular reviewed in~\citep{gutig_spike_2014}. The Tempotron is a supervised synaptic learning algorithm which classifies a distractor from a target motif. This aims at extending the perceptron which does not incorporate a spike timing framework. The tempotron learning rule is derived by an optimization process and takes the form of a STDP rule. It is general consensus that spike timing (STDP) plays a crucial role in the development of synaptic efficacy for many different kinds of neurons~\citep{caporale_spike_2008}. The limits of this model is that it's output is only binary and that it's storage capacity are limited.
The recent ``multi-neuronal spike sequence detector'' (MNSD) architecture integrates the weight- and delay-adjustment methods by combining plasticity with the neurocomputational feature spike latency : \url{https://pubmed.ncbi.nlm.nih.gov/33679293/}
an extensive (graph-centric) review on \href{https://arxiv.org/abs/2109.07618}{Synchronization in time-varying networks}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extensions of Izhikevitch's polychronization model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A notable exception is an extensive work aiming at reproducing the polychronization model~\citep{pauli_reproducing_2018}. Indeed, the original paper contained material within the text to reproduce the whole model. This more recent work details how this code was slighlty corrected. It comes with python code and a version control system detailing the whole process used to give provenance to the different steps in this scientific process.

A Bayesian account: ``Previous methods for studying the PNG activation response to stimuli have been limited by the template-based methods used to identify PNG activation. In this letter, we outline a new method that overcomes these difficulties by establishing for the first time a probabilistic interpretation of PNG activation. We then demonstrate the use of this method by investigating the claim that PNGs might provide the foundation of a representational system.''~\citep{guise_bayesian_2014}. Stimulation of a trained network produces the activation of a PNG, ie the propagation of firing activity through multiple layers due to convergent patterns of firing.

% STDP based
Memory traces in dynamical systems~\citep{ganguli_memory_2008} : ``To perform nontrivial, real-time computations on a sensory input stream, biological systems must retain a short-term memory trace of their recent inputs. It has been proposed that generic high-dimensional dynamical systems could retain a memory trace for past inputs in their current state. This raises important questions about the fundamental limits of such memory traces and the properties required of dynamical systems to achieve these limits. We address these issues by applying Fisher information theory to dynamical systems driven by time-dependent signals corrupted by noise. We introduce the Fisher Memory Curve (FMC) as a measure of the signal-to-noise ratio (SNR) embedded in the dynamical state relative to the input SNR. The integrated FMC indicates the total memory capacity. We apply this theory to linear neural networks and show that the capacity of networks with normal connectivity matrices is exactly 1 and that of any network of N neurons is, at most, N. A nonnormal network achieving this bound is subject to stringent design constraints: It must have a hidden feedforward architecture that superlinearly amplifies its input for a time of order N, and the input connectivity must optimally match this architecture. The memory capacity of networks subject to saturating nonlinearities is further limited, and cannot exceed $\sqrt N$. This limit can be realized by feedforward structures with divergent fan out that distributes the signal across neurons, thereby avoiding saturation. We illustrate the generality of the theory by showing that memory in fluid systems can be sustained by transient nonnormal amplification due to convective instability or the onset of turbulence.''

We address these issues by applying Fisher information theory to dynamical systems driven by time-dependent signals corrupted by noise. Memory capacity is constrained by architecture: ``This limit can be realized by feedforward structures with divergent fan out that distributes the signal across neurons, thereby avoiding saturation.''

Some other models of latency motifs detection using STDP learning rules. For instance,~\citep{kheradpisheh_stdp-based_2018} implements a STDP-based spiking deep convolutional neural networks for object recognition;~\citep{tavanaei_representation_2018} develops a form of spike-based, competitive learning applied for unsupervised learning. In~\citep{russo_cell_2017}, authors developed novel machine learning tools and statistical tests for unsupervised spatio-temporal pattern detection in non-stationary environments, which was applied to simultaneous electrophysiological recordings from tens to hundreds of neurons for decoding cognitive processes from neural activity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Application to Image processing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Application to Image processing using sparse spiking representations: Using the core computational unit defined, extension of the computation to a topographic representation similar to that observed in the primary visual cortex of mammals. design of micro-circuits with specific lateral interactions will allow us to design efficient micro-circuits for the sparse representation of images.

there are temporal delays in the nervous system, both at the neural~\citep{perrinet_active_2014} and behavioral~\citep{khoei_flash-lag_2017} levels. Extending this knowledge to the optimization of delays in a SNN will provide a breakthrough in the efficiency of these networks.

may be used for motion detection and interpolation~\citep{kaplan_anisotropic_2013}~\citep{khoei_flash-lag_2017}

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Precise spiking motifs in neurobiology}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Learning weights \ldots{} and delays}\label{learning-weights-and-delays}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
spike time coding in a neuron: We will describe the Spike-Time Dependent Plasticity (STDP)~\citep{markram_regulation_1997} rule which implement an unsupervised learning aiming at optimizing the detection of polychronous patterns, that is volleys of spikes which are synchronized, up to some stable pattern of pre-synaptic delays. This STDP rule will be based by the inversion of the generative model for spike formation and will therefore be derived by a Bayesian approach. This will decouple the active synapses (similarly to a logistic regression) from the values of possible synaptic delays.

\begin{itemize}
 \item
 ~\citep{perrinet_coherence_2002} : coherence detection
\item
 ~\citep{perrinet_networks_2001} : STDP
\item
  Masquelier, Gilson et al.~- 2010 - STDP in Recurrent Neuronal Networks~\citep{gilson_stdp_2010} or Delay Selection by Spike-Timing-Dependent Plasticity in Recurrent Networks of Spiking Neurons Receiving Oscillatory Inputs. PLoS Comput Biol 9(2): e1002897.~\citep{kerr_delay_2013} which targets at the selective potentiation of recurrent connections with different axonal and dendritic delays during oscillatory activity.
\end{itemize}

Our ability to track and respond to rapidly changing visual stimuli, such as a fast-moving tennis ball, indicates that the brain is capable of extrapolating the trajectory of a moving object to predict its current position, despite the delays that result from neural transmission. Here, we show how the neural circuits underlying this ability can be learned through spike-timing-dependent synaptic plasticity and that these circuits emerge spontaneously and without supervision. This demonstrates how the neural transmission delays can, in part, be compensated to implement the extrapolation mechanisms required to predict where a moving object is at the present moment.~\citep{burkitt_predictive_2021}

~\citep{nadafian_bio-plausible_2020}

Bio-plausible Unsupervised Delay Learning for Extracting Temporal Features in Spiking Neural Networks
Alireza Nadafian, Mohammad Ganjtabesh

\begin{verbatim}
The plasticity of the conduction delay between neurons plays a fundamental role in learning. However, the exact underlying mechanisms in the brain for this modulation is still an open problem. Understanding the precise adjustment of synaptic delays could help us in developing effective brain-inspired computational models in providing aligned insights with the experimental evidence. In this paper, we propose an unsupervised biologically plausible learning rule for adjusting the synaptic delays in spiking neural networks. Then, we provided some mathematical proofs to show that our learning rule gives a neuron the ability to learn repeating spatio-temporal patterns. Furthermore, the experimental results of applying an STDP-based spiking neural network equipped with our proposed delay learning rule on Random Dot Kinematogram indicate the efficacy of the proposed delay learning rule in extracting temporal features.
\end{verbatim}

Integrating synaptic delay plasticity into supervised learning and proposes a novel learning method that adjusts both the synaptic delays and weights of the learning neurons to make them fire precisely timed spikes, that is referred to as synaptic delay-weight plasticity~\citep{zhang_supervised_2020}. Uses synthetic data to extend the existing Remote Supervised Method (ReSuMe) method.

In a recent paper~\citep{luo_supervised_2022}, authors propose a gradient descent-based learning algorithm for synaptic delays to enhance the sequential learning performance of single spiking neuron. In this algorithm, information is encoded in the relative timing of individual neuronal spikes, and learning is performed based on the exact derivatives of the postsynaptic spike times with respect to presynaptic spike times.

In a computational model, authors show that the frequently activated polychronous neural groups can be learned by readout neurons with joint weight-delay spike-timing-dependent plasticity~\citep{sun_learning_2016}. This uses a joint Weight-Delay Spike-Timing-Dependent Plasticity and show aan efficient learning of polychronous groups.

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Learning sequences}\label{learning-sequences}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In~\citep{duffy_variation_2019}, authors present a model to ``show a way by which the nervous system maintains precise, stereotyped behavior in the face of environmental and neural changes.'' It is shown in bridsong generation that ``A precise, temporally sparse sequence from the premotor nucleus HVC is crucial to the performance of song in songbirds''~\citep{suthers_motor_2002,wild_descending_1993,yu_temporal_1996} and this model shows how one could vary HVC activity using something similar to dropout in ML. Using such controlled variability, ``behaviors are made more robust to environmental change by continually seeking subtly new ways of performing the same task.'' Not sure however how important it is that the HVC pattern should be sparse (and similar to PGs).

\begin{itemize}
\item
  in~\citep{agus_rapid_2010}, there are ``good'' and ``bad'' noises show that some patterns are more easy to disentangle - similar to bird songs and ecological niche.
\item
  In Bellec~\citep{bellec_fitting_2021}, authors fit summary statistics of neural data with a differentiable spiking network simulator.

  \begin{itemize}
     \item
    the loss function is the cross entropy (following Bernouilli hypothesis with a GLM where each unit is modelled with a SRM neuron~\citep{gerstner_time_1995} with recurrent dynamics)
  \item
    sample and measure method to include latent / hidden neurons
  \item
    comes with code \url{https://github.com/EPFL-LCN/pub-bellec-wang-2021-sample-and-measure}
  \item
    V1-dataset : The dataset we used was collected by Smith and Kohn 49 and is publicly available at:
     \url{http://crcns.org/data-sets/vc/pvc-11} - it is in a sense supervised with the input being the movie and the output the spikes recorded.
  \end{itemize}
\end{itemize}

A recent work~\citep{ghosh_spatiotemporal_2019} proposes a two-stage unsupervised-supervised system for the categorization of spatiotemporal actions from an event-based stream. The first stage learns spatiotemporal convolutional filters targeted to minimize event-removal related changes to a local spatiotemporal spike-event pattern. The second stage takes the output of the spatiotemporal filters as an input example containing multiple feature channels, and proceeds to train a classifier for recognition of spatiotemporal activity. For testing the system, two datasets are considered: DVS Gesture and a new action recognition dataset recorded for this work. Results demonstrate the ability of the system to outperform the state-of-the-art in event-based gesture recognition, along with demonstrating superior performance to other alternative ways of obtaining the first stage filters. Showing the potential of such representation

Learning compositional sequences with multiple time scales through a hierarchical network of spiking neurons.
Maes A, Barahona M, Clopath C.PLoS Comput Biol. 2021

Characteristics of sequential activity in networks with temporally asymmetric Hebbian learning.
Gillett M, Pereira U, Brunel N.Proc Natl Acad Sci U S A. 2020

Unsupervised Learning of Persistent and Sequential Activity.
Pereira U, Brunel N.Front Comput Neurosci. 2020

From space to time: Spatial inhomogeneities lead to the emergence of spatiotemporal sequences in spiking neuronal networks.
Spreizer S, Aertsen A, Kumar A.PLoS Comput Biol. 2019

Fast and flexible sequence induction in spiking neural networks via rapid excitability changes.
Pang R, Fairhall AL.Elife. 2019 May~\citep{pang_fast_2019}

Emergence of spontaneous assembly activity in developing neural networks without afferent input.
Triplett MA, Avitan L, Goodhill GJ.PLoS Comput Biol. 2018

Training and Spontaneous Reinforcement of Neuronal Assemblies by Spike Timing Plasticity.
Ocker GK, Doiron B.Cereb Cortex. 2019.

>>>>

Considering the number of spikes required to exceed a voltage threshold, asynchronous signals are less efficient than synchronous signals. However, taking axonal propagation times into account, synchronous signals may not coincide significantly at the post-synaptic neuron contrary to asynchronous or polychronous signals. The term polychronous was first introduced by~\citet{izhikevich_polychronization_2006}. He defines this term after pointing out a particular organization of the neurons of his spiking artificial neural network. The network is characterized by a timing-dependant learning rule for weights (STDP)~\citep{markram_regulation_1997} and by fixed conduction delays between neurons. It is general consensus that spike timing (STDP) plays a crucial role in the development of synaptic efficacy for many different kinds of neurons~\citep{caporale_spike_2008}. Due to the interplay between the delays and STDP, the spiking neurons spontaneously self-organize into groups and generate patterns of stereotypical polychronous activity, i.e.~exhibit reproducible time-locked but not synchronous firing patterns. The neurons composing a group discharge at different times, but due to delays, the spikes reach the postsynaptic neuron at the same time. This synchrony leads to the summation of the excitatory post-synaptic potentials evoked by each spike and thus to the crossing of the voltage threshold and to the discharge of a spike. According to the STDP rule, the neurons involved in this activity will see their weight of synaptic connection increase and thus, constitute a polychronous group. Interestingly, thanks to the fact that a neuron can be involved in different polychronous groups, the number of coexisting polychronous groups far exceeds the number of neurons in the network, resulting in an unprecedented memory capacity of the system.

@@

% polychronization
Interestingly the paper by~\citet{izhikevich_polychronization_2006} stirred a lively debate in the field of computational neuroscience, with a general postive acceptance, but quite few works extended this seminal paper.
Indeed, there were already existing models of synaptic delay learning in spiking neural networks, see for instance~\citep{huning_synaptic_1998} or~\citep{eurich_dynamics_1999} yet they had not shown potential applications to the deterction of spiking motifs. A popular model for the detection of latency patterns is the \emph{tempotron}~\citep{gutig_tempotron_2006}. This model is in particular reviewed in~\citep{gutig_spike_2014}. The Tempotron is a supervised synaptic learning algorithm which classifies a distractor from a target motif. This aims at extending the perceptron which does not incorporate a spike timing framework. The tempotron learning rule is derived by an optimization process and takes the form of a STDP rule.  The limits of this model is that it's output is only binary and that it's storage capacity are limited.
The recent ``multi-neuronal spike sequence detector'' (MNSD) architecture integrates the weight- and delay-adjustment methods by combining plasticity with the neurocomputational feature spike latency~\citep{susi_nmnsd-spiking_2021}.
The recent ``multi-neuronal spike sequence detector'' (MNSD) architecture integrates the weight- and delay-adjustment methods by combining plasticity with the neurocomputational feature spike latency~\citep{susi_nmnsd-spiking_2021}. See also the extensive (graph-centric) review on synchronization in time-varying networks~\citep{ghosh_synchronized_2022}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extensions of Izhikevitch's polychronization model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
A notable extension of~\citep{izhikevich_polychronization_2006} is an extensive work aiming at reproducing the polychronization model~\citep{pauli_reproducing_2018}. Indeed, while the original paper contained material within the text to reproduce the whole model, it was not complete for the repoduction of all results presented in that manuscript. This more recent work details how this code was slighlty corrected. It comes with python code and a version control system detailing the whole process used to give provenance to the different steps in this scientific process.

Another recent work gives a Bayesian account in a similar model~\citep{guise_bayesian_2014}. Based on the fact that previous methods for studying polychronous neural groups (PNG) activation response to stimuli have been limited by the template-based methods used to identify PNG activation, authors outline a new method that overcomes these difficulties by establishing a probabilistic interpretation of PNG activation. They demonstrate the use of this method by investigating the claim that PNGs might provide the foundation of a representational system. Stimulations of the trained network produces the activation of a PNG, ie the propagation of firing activity through multiple layers due to convergent patterns of firing.

% STDP based
%Memory traces in dynamical systems~\citep{ganguli_memory_2008} : ``To perform nontrivial, real-time computations on a sensory input stream, biological systems must retain a short-term memory trace of their recent inputs. It has been proposed that generic high-dimensional dynamical systems could retain a memory trace for past inputs in their current state. This raises important questions about the fundamental limits of such memory traces and the properties required of dynamical systems to achieve these limits. We address these issues by applying Fisher information theory to dynamical systems driven by time-dependent signals corrupted by noise. We introduce the Fisher Memory Curve (FMC) as a measure of the signal-to-noise ratio (SNR) embedded in the dynamical state relative to the input SNR. The integrated FMC indicates the total memory capacity. We apply this theory to linear neural networks and show that the capacity of networks with normal connectivity matrices is exactly 1 and that of any network of N neurons is, at most, N. A nonnormal network achieving this bound is subject to stringent design constraints: It must have a hidden feedforward architecture that superlinearly amplifies its input for a time of order N, and the input connectivity must optimally match this architecture. The memory capacity of networks subject to saturating nonlinearities is further limited, and cannot exceed $\sqrt N$. This limit can be realized by feedforward structures with divergent fan out that distributes the signal across neurons, thereby avoiding saturation. We illustrate the generality of the theory by showing that memory in fluid systems can be sustained by transient nonnormal amplification due to convective instability or the onset of turbulence.'' We address these issues by applying Fisher information theory to dynamical systems driven by time-dependent signals corrupted by noise. Memory capacity is constrained by architecture: ``This limit can be realized by feedforward structures with divergent fan out that distributes the signal across neurons, thereby avoiding saturation.''

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Learning synaptic delays}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A whole range of models of latency motifs detection are using STDP-based learning rules. For instance,~\citep{kheradpisheh_stdp-based_2018} implements a STDP-based spiking deep convolutional neural networks for object recognition;~\citep{tavanaei_representation_2018} develops a form of spike-based, competitive learning applied for unsupervised learning. In~\citep{russo_cell_2017}, authors developed novel machine learning tools and statistical tests for unsupervised spatio-temporal pattern detection in non-stationary environments, which was applied to simultaneous electrophysiological recordings from tens to hundreds of neurons for decoding cognitive processes from neural activity.
%
Modified STPD rules have been used for synchronous coherence detection~\citep{perrinet_coherence_2002}, for the learning of specific recetpive fields~\citep{perrinet_networks_2001} and were also extended to recurrent Neuronal Networks~\citep{gilson_stdp_2010} or delay selection in recurrent networks of spiking neurons receiving oscillatory inputs\citep{kerr_delay_2013} which targets at the selective potentiation of recurrent connections with different axonal and dendritic delays during oscillatory activity. More generally, our ability to track and respond to rapidly changing visual stimuli, such as a fast-moving tennis ball, indicates that the brain is capable of extrapolating the trajectory of a moving object to predict its current position, despite the delays that result from neural transmission. Here, we show how the neural circuits underlying this ability can be learned through spike-timing-dependent synaptic plasticity and that these circuits emerge spontaneously and without supervision. This demonstrates how the neural transmission delays can, in part, be compensated to implement the extrapolation mechanisms required to predict where a moving object is at the present moment.~\citep{burkitt_predictive_2021}

Specifically, a recent work proposed a bio-plausible unsupervised delay learning for extracting temporal features in spiking neural networks~\citep{nadafian_bio-plausible_2020}. Authors provided some mathematical proofs to show that our learning rule gives a neuron the ability to learn repeating spatio-temporal patterns. Furthermore, the experimental results of applying an STDP-based spiking neural network was applied on Random Dot Kinematogram. Another model of synaptic delay-weight plasticity~\citep{zhang_supervised_2020} integrates synaptic delay plasticity into supervised learning and proposes a novel learning method that adjusts both the synaptic delays and weights of the learning neurons to make them fire precisely timed spikes. % Uses synthetic data to extend the existing Remote Supervised Method (ReSuMe) method.
In a recent paper~\citep{luo_supervised_2022}, authors propose a gradient descent-based learning algorithm for synaptic delays to enhance the sequential learning performance of single spiking neuron. In this algorithm, information is encoded in the relative timing of individual neuronal spikes, and learning is performed based on the exact derivatives of the postsynaptic spike times with respect to presynaptic spike times.
In yet another computational model,~\citet{sun_learning_2016} show that the frequently activated polychronous neural groups can be learned by readout neurons with joint weight-delay spike-timing-dependent plasticity. This uses a joint Weight-Delay Spike-Timing-Dependent Plasticity and show aan efficient learning of polychronous groups.

%In~\citep{duffy_variation_2019}, authors present a model to ``show a way by which the nervous system maintains precise, stereotyped behavior in the face of environmental and neural changes.'' It is shown in birdsong generation that ``A precise, temporally sparse sequence from the premotor nucleus HVC is crucial to the performance of song in songbirds''~\citep{suthers_motor_2002,wild_descending_1993,yu_temporal_1996} and this model shows how one could vary HVC activity using something similar to dropout in ML. Using such controlled variability, ``behaviors are made more robust to environmental change by continually seeking subtly new ways of performing the same task.'' Not sure however how important it is that the HVC pattern should be sparse (and similar to PGs). In~\citep{agus_rapid_2010}, there are ``good'' and ``bad'' noises show that some patterns are more easy to disentangle - similar to bird songs and ecological niche.

% Learning compositional sequences with multiple time scales through a hierarchical network of spiking neurons.
% Maes A, Barahona M, Clopath C.PLoS Comput Biol. 2021

% Characteristics of sequential activity in networks with temporally asymmetric Hebbian learning.
% Gillett M, Pereira U, Brunel N.Proc Natl Acad Sci U S A. 2020

% Unsupervised Learning of Persistent and Sequential Activity.
% Pereira U, Brunel N.Front Comput Neurosci. 2020

% From space to time: Spatial inhomogeneities lead to the emergence of spatiotemporal sequences in spiking neuronal networks.
% Spreizer S, Aertsen A, Kumar A.PLoS Comput Biol. 2019

% Fast and flexible sequence induction in spiking neural networks via rapid excitability changes.
% Pang R, Fairhall AL.Elife. 2019 May~\citep{pang_fast_2019}

% Emergence of spontaneous assembly activity in developing neural networks without afferent input.
% Triplett MA, Avitan L, Goodhill GJ.PLoS Comput Biol. 2018

% Training and Spontaneous Reinforcement of Neuronal Assemblies by Spike Timing Plasticity.
% Ocker GK, Doiron B.Cereb Cortex. 2019.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Real-world applications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Most of these theoretical models are trying to reproduce neurobiological observations and some others also propose applications to machine learning mothods such as image processing. For instance, in a recent work~\citet{ghosh_spatiotemporal_2019} propose a two-stage unsupervised-supervised system for the categorization of spatiotemporal actions from an event-based stream. The first stage learns spatiotemporal convolutional filters targeted to minimize event-removal related changes to a local spatiotemporal spike-event pattern. The second stage takes the output of the spatiotemporal filters as an input example containing multiple feature channels, and proceeds to train a classifier for recognition of spatiotemporal activity. For testing the system, two datasets are considered: DVS Gesture and a new action recognition dataset recorded for this work. Results demonstrate the ability of the system to outperform the state-of-the-art in event-based gesture recognition, along with demonstrating superior performance to other alternative ways of obtaining the first stage filters. Showing the potential of such representation

There are more applications to image processing using sparse spiking representations. Using the core computational unit defined, extension of the computation to a topographic representation similar to that observed in the primary visual cortex of mammals. design of micro-circuits with specific lateral interactions will allow us to design efficient micro-circuits for the sparse representation of images.

there are temporal delays in the nervous system, both at the neural~\citep{perrinet_active_2014}

and behavioral~\citep{khoei_flash-lag_2017} levels. Extending this knowledge to the optimization of delays in a SNN will provide a breakthrough in the efficiency of these networks.

may be used for motion detection and Motion-based prediction explains the role of tracking in motion extrapolation interpolation~\citep{kaplan_anisotropic_2013}~\citep{khoei_flash-lag_2017}

We will review some more applications of using precise spiking motifs in neuromorphic engineering, but will first review current evidence in neurobiology, that is, from actual recordings in biological tissues.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Precise spiking motifs in neurobiology}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 In Bellec~\citep{bellec_fitting_2021}, authors fit summary statistics of neural data with a differentiable spiking network simulator. The loss function is the cross entropy (following Bernouilli hypothesis with a GLM where each unit is modelled with a SRM neuron~\citep{gerstner_time_1995} with recurrent dynamics). The model uses samples and measure method sto include latent / hidden neurons. In particular, it    comes with  \href{code}{https://github.com/EPFL-LCN/pub-bellec-wang-2021-sample-and-measure}. It uses the publicly available \href{V1-dataset}{http://crcns.org/data-sets/vc/pvc-11}, which allows to supervise the model with the input being the movie and the output the spikes recorded.

@@
